The Sub-Millimetre User Reduction Facility: an iterative map-maker for \scuba

### 2012-08-10 smurf_paper.tex
re-do plots for intro (time-series and power spec), new and old s2sro data

\begin{figure}
\vspace{2cm}
\textbf{This will be a figure showing s4a and s8d responsivity maps}
\vspace{2cm}
\caption{The response of each bolometer to known input heater power
  for a typical night during S2SRO. The s4a subarray had a
  particularly large variation in $T_\mathrm{C}$ towards the
  bottom-right which resulted in lower responsivity, and
  correspondingly larger noise. The s8d array also suffered
  significant variations across the focal plane, in particular
  removing larger number of useful detectors from the bottom-left.}
\label{fig:sensitivities}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{bolos_point_mix.pdf}
\caption{A comparison between single bolometer time series in each
  band (top two plots), with the mixing chamber temperature and
  azimuth/elevation pointing offsets. There is a strong correlation
  between the bolometers and the roughly $\sim$25\,s oscillation in
  the fridge, but not with the telescope motion. Also note that the
  total power in this primary signal is similar at both 450 and
  850\,\micron, pointing to an internal rather than an external
  source. The grey signals overplotted in the top-two panels show the
  residual time-series after removing the common-mode signal. This
  operation shows: (i) that most of the low-frequency signal is common
  to all of the bolometers; and (ii) the non-correlated, and
  predominantly white noise at 450\,\micron\ is significantly larger
  than at 850\,\micron.}
\label{fig:bolos_mix}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{pspec.pdf}
\caption{Bolometer power spectral densities. Four representative
  bolometers have been selected from each sub-array, and the
  flat-fielded (but otherwise raw) PSDs are shown as coloured dotted
  lines (the blue signals are for the same time series as those shown
  in Fig.~\ref{fig:bolos_mix}). Horizontal dotted lines at $5 \times
  10^{-8}$ and $5 \times 10^{-9}$\,pW\,Hz$^{-1}$ at 450 and
  850\,\micron\ respectively, give the approximate white-noise
  levels. There are broad line features in the PSDs at both
  wavelengths above $\sim$35\,Hz. From $\sim$50\,Hz up to the Nyquist
  frequency, the gradual roll-off of the anti-aliasing filter is also
  evident.  At lower frequencies, the bolometer signals exhibit clear
  $1/f$ knees at approximately 2 and 4\,Hz at 450 and
  850\,\micron. The solid black lines are the PSDs of the common-mode
  signals at each wavelength, and the solid coloured lines show the
  PSDs of the bolometers once the common-mode is removed. These
  residual signals have significantly lower $1/f$ knees, approximately
  0.4 and 2\,Hz at 450 and 850\,\micron. Finally, the dashed black
  lines show the spectral shape produced by a point source, assuming
  that the telescope is slewing at 200\,arcsec\,sec$^{-1}$ (typical
  for S2SRO); for reference, the top horizontal axis shows the
  conversion from frequency to angular scale. We can see that the line
  features may add significant noise on the scale of the PSF. We also
  see that, for this scan velocity, the low-frequency noise begins to
  dominate on scales of approximately 8.3 and 1.7\,arcmin; these scales
  are comparable to the array footprint.}
\label{fig:pspec}
\end{figure}

>>>>

%\begin{figure}
%\vspace{2cm}
%\textbf{This will be a figure showing s4a and s8d responsivity maps}
%\vspace{2cm}
%\caption{The response of each bolometer to known input heater power
%  for a typical night during S2SRO. The s4a subarray had a
%  particularly large variation in $T_\mathrm{C}$ towards the
%  bottom-right which resulted in lower responsivity, and
%  correspondingly larger noise. The s8d array also suffered
%  significant variations across the focal plane, in particular
%  removing larger number of useful detectors from the bottom-left.}
%\label{fig:sensitivities}
%\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.49\linewidth]{bolos_point_mix_s2sro.pdf}
\includegraphics[width=0.49\linewidth]{bolos_point_mix.pdf}
\caption{A comparison between single bolometer time series in each
  band (top two plots), with the mixing chamber temperature and
  azimuth/elevation pointing offsets. There is a strong correlation
  between the bolometers and the roughly $\sim$25\,s oscillation in
  the fridge, but not with the telescope motion. Also note that the
  total power in this primary signal is similar at both 450 and
  850\,\micron, pointing to an internal rather than an external
  source. The grey signals overplotted in the top-two panels show the
  residual time-series after removing the common-mode signal. This
  operation shows: (i) that most of the low-frequency signal is common
  to all of the bolometers; and (ii) the non-correlated, and
  predominantly white noise at 450\,\micron\ is significantly larger
  than at 850\,\micron.}
\label{fig:bolos_mix}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.49\linewidth]{pspec_s2sro.pdf}
\includegraphics[width=0.49\linewidth]{pspec.pdf}
\caption{Bolometer power spectral densities. Four representative
  bolometers have been selected from each sub-array, and the
  flat-fielded (but otherwise raw) PSDs are shown as coloured dotted
  lines (the blue signals are for the same time series as those shown
  in Fig.~\ref{fig:bolos_mix}). Horizontal dotted lines at $5 \times
  10^{-8}$ and $5 \times 10^{-9}$\,pW\,Hz$^{-1}$ at 450 and
  850\,\micron\ respectively, give the approximate white-noise
  levels. There are broad line features in the PSDs at both
  wavelengths above $\sim$35\,Hz. From $\sim$50\,Hz up to the Nyquist
  frequency, the gradual roll-off of the anti-aliasing filter is also
  evident.  At lower frequencies, the bolometer signals exhibit clear
  $1/f$ knees at approximately 2 and 4\,Hz at 450 and
  850\,\micron. The solid black lines are the PSDs of the common-mode
  signals at each wavelength, and the solid coloured lines show the
  PSDs of the bolometers once the common-mode is removed. These
  residual signals have significantly lower $1/f$ knees, approximately
  0.4 and 2\,Hz at 450 and 850\,\micron. Finally, the dashed black
  lines show the spectral shape produced by a point source, assuming
  that the telescope is slewing at 200\,arcsec\,sec$^{-1}$ (typical
  for S2SRO); for reference, the top horizontal axis shows the
  conversion from frequency to angular scale. We can see that the line
  features may add significant noise on the scale of the PSF. We also
  see that, for this scan velocity, the low-frequency noise begins to
  dominate on scales of approximately 8.3 and 1.7\,arcmin; these scales
  are comparable to the array footprint.}
\label{fig:pspec}
\end{figure*}
